My first knitr document
---

This is text

```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```

```{r secoindpart}
set.seed(1)
x <- rnorm(200)
mean(x)
```

pas d'echo pour simu

```{r simulation, echo=FALSE}
set.seed(1)
x <- rnorm(2300)
mean(x)
```

pas de res pour simu2

```{r simulation2, echo=TRUE, results='hide'}
set.seed(1)
x <- rnorm(2300)
mean(x)
```


#In line text computation

```{r sim, echo=FALSE, results='hide'}
time  <- format(Sys.time(), "%a %b %d %X %Y")
rand <- rnorm(1)
```

  
Affiche les variables time :  `r time` et aussi my favorite random nb : `r rand` xxx


##Incorporating graphique

Let's first simulate data
```{r simudata, echo=TRUE}
x  <- rnorm(100); y <- x+ rnorm(100, sd=0.5)
```
Here is a scaterplot of the data
```{r scatterplot, fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y, main = "mes data")
```


##Making Table

Let's first simulate data
Linear model

```{r}
library(datasets)
data(airquality)
fit <- lm(Ozone ~ Solar.R + Wind + Temp, data = airquality)
```
Here is a table of linear regression coefficients
```{r showtable, results='asis'}
library(xtable)
xt <- xtable(summary(fit))
print(xt,type = "html")
```


#Settiong global option
at the top of the doc???
```{r setoptions, echo=FALSE}
library(knitr)
opts_chunk$set(echo = FALSE, results = "hide")
```
on ne voit rien
```{r}
set.seed(1)
x <- rnorm(100)
mean(x)
```
on voit code mais pas results
```{r echo=TRUE}
set.seed(1)
x <- rnorm(100)
mean(x)
```


Let's first simulate data
```{r simudatabis, echo=TRUE}
x  <- rnorm(100); y <- x+ rnorm(100, sd=0.5)
```
Here is a scaterplot of the data
```{r scatterplotbis, fig.height=4}
par(mar = c(5,4,1,1), las = 1)
plot(x,y, main = "mes data")
```
